Using Constraint Programming to Generate Random Logic Programs

### 2019-12-24 paper/paper.tex
More restructuring

@@

\begin{itemize}
\item Show that the set of all ProbLog programs is equal to the set of programs
  I can generate (alternatively, show that, given any ProbLog program, there are
  parameter values high enough to generate it).
\item Given fixed parameters, use combinatorial arguments to calculate how many
  different programs there are and check that I'm generating the same number.
\end{itemize}

>>>>

\section{Introduction}

Motivation:
\begin{itemize}
\item Generating random programs that generate random data.
  %For example, enforcing that the decision is independent of gender.
\item Learning: how this can be used for (targeted) learning, when (atomic)
  probabilities can be assigned based on counting and we can have extra
  constraints. A more primitive angle: generate structures, learn weights.
\end{itemize}

@@

\begin{itemize}
\item Support for constants and multiple variables.
  \begin{itemize}
  \item Each clause is defined for each predicate with standard variable names
    (X, Y, etc.).
  \item There is a list of constants and a list of predicates with their
    arities. Maybe also a list of variables.
  \end{itemize}
\item Make negative cycle detection use the graph representation.
\item Finish the propagation algorithm for conditional independence. The
  propagation algorithm for independence is extended with masks that are either
  potential or definite. Masking happens in two stages: first, we mask
  expressions within formulas, and then predicates. Masking algorithm uses an
  algorithm for perfect bipartite matching.
\item Show that the set of all ProbLog programs is equal to the set of programs
  I can generate (alternatively, show that, given any ProbLog program, there are
  parameter values high enough to generate it).
\item Given fixed parameters, use combinatorial arguments to calculate how many
  different programs there are and check that I'm generating the same number.
\end{itemize}
